Combinatorial Proofs and Decomposition Theorems for First-order Logic

### 2021-01-14 main.tex
some defs

\usepackage{tikz}
\usepackage{amsthm}\theoremstyle{plain}
\newtheorem{thm}{Theorem}%[section]

\theoremstyle{definition}
\newtheorem{definition}[thm]{Definition}
\newtheorem{lemma}[thm]{Lemma}
\newtheorem{notation}[thm]{Notation}
\newtheorem{proposition}[thm]{Proposition}
\newtheorem{theorem_}[thm]{Theorem}
\newtheorem{example}[thm]{Example}
\newtheorem{remark}[thm]{Remark}

@@

A derivation $\Deri$ is \bfit{rectified} if every line in $\Deri$ is rectified.

\todo{define rectification $\rectif\Deri$ of a derivation  $~\vlder{\FOMLS}{\Deri}{A}{\ttt}$}
\todo{define substitution of a derivation $\substof{\Deri}$ and linking of a derivation $\linkingof{\Deri}$ }

\begin{thm}
  Let the derivation $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ be given. Then
  the graph $\graphof{\rectif A}$ forms a fonet whose linking is
  $\linkingof{\rectif\Deri}$ and whose dualizer is
  $\substof{\rectif\Deri}$.
\end{thm}

@@

\begin{thm}
  Let $\gC$ be a fonet with linking $\linkingof\gC$ and dualizer
  $\delta$, and let $A$ be a formula with $\graphof A=\gC$.  Then
  there is a derivation $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ such that
  $\linkingof\gC=\linkingof{\Deri}$ and $\delta=\substof{\Deri}$.
\end{thm}

@@

\begin{theorem_}
\label{thm1}
Let $\Gamma$ be a sequent. Then there is a proof of $\Pi$ in $\LKm$ iff there is a proof of some sequent $\Delta$ in $\FOMLLm$ and a derivation from $\Delta$ to $\Gamma$ consisting of the $\cD$ and $\wD$ rules only. 
\end{theorem_}

>>>>

\usepackage{tikz}
\usepackage{amsthm}\theoremstyle{plain}
\newtheorem{thm}{Theorem}%[section]
\newtheorem{lemma}[thm]{Lemma}
\newtheorem{proposition}[thm]{Proposition}
\newtheorem{theorem_}[thm]{Theorem}

\theoremstyle{definition}
\newtheorem{definition}[thm]{Definition}
\newtheorem{notation}[thm]{Notation}
\newtheorem{example}[thm]{Example}
\newtheorem{remark}[thm]{Remark}

@@

A derivation $\Deri$ is \bfit{rectified} if every line in $\Deri$ is
rectified.  For a non-rectified derivation $\Deri$ in $\FOMLS$ we can
define its \bfit{rectification} $\rectif\Deri$ by recifying each
line. In $\FOMLS$ this can be done inductively, proceeding step-wise
from conclusion to premise, as the only rules involving bound
variables are $\forall$ and $\exists$ which both remove a binder (and
all occurrences of the variable it binds).\footnote{As for formulas,
the rectification of a derivation is unique up to renaming of bound
variables.}\todo{check if we need that $\Deri$ has premise $\ttt$}.

A derivation $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ determines a
substitution which maps the existential bound variables occurring in
$A$ to the terms substituted for them in the instances of the
$\exists$-rule in $\Phi$. We denote this substitution with
$\substof\Phi$. Furthermore, every atom occuring in the conclusion $A$
must be consumed by a unique instance of the rule $\aiD$ in
$\Deri$. This allows us to define a (partial) equivalence relation
$\linkingof\Deri$ on the atom occurrences in $A$ by $a\linkingof\Deri
b$ if $a$ and $b$ are consumed by the same instance of $\aiD$
in~$\Deri$. We call $\linkingof\Deri$ the \bfit{linking} of~$\Deri$.

\todo{examle here}

\begin{lemma}\label{lem:MLS1->fonet}
  Let $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ be a recified derivation. Then
  the graph $\graphof{A}$ forms a fonet whose linking is
  $\linkingof{\Deri}$ and whose dualizer is
  $\substof{\Deri}$.
\end{lemma}

@@

\begin{thm}
  Let $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ be given. Then
  the graph $\graphof{\rectif A}$ forms a fonet whose linking is
  $\linkingof{\rectif\Deri}$ and whose dualizer is
  $\substof{\rectif\Deri}$.
\end{thm}

\begin{proof}
  Apply Lemma~\ref{lem:MLS1->fonet} to the rectification $\rectif\Deri$ of $\Deri$.
\end{proof}

\begin{thm}
  Let $\gC$ be a fonet with linking $\linkingof\gC$, let $\delta$ be a dualizer
  for $\gC$, and let $A$ be a formula with $\graphof A=\gC$.  Then
  there is a derivation $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ such that
  $\linkingof\gC=\linkingof{\Deri}$ and $\delta=\substof{\Deri}$.
\end{thm}

@@

\begin{thm}
\label{thm1}
Let $\Gamma$ be a sequent. Then there is a proof of $\Pi$ in $\LKm$ iff there is a proof of some sequent $\Delta$ in $\FOMLLm$ and a derivation from $\Delta$ to $\Gamma$ consisting of the $\cD$ and $\wD$ rules only. 
\end{thm}
